Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Young Validated Saturn-Sized Planet in IC~2602

### 2020-07-21 paper/ms.tex
update manuscript

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II.
  TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602
}

@@

Over the first 100 million years of their lives, exoplanet systems are
expected to undergo major physical and dynamical changes.  For a
typical Sun-like star, the protoplanetary disk disperses within
roughly 1--10 million years
\citep{mamajek_initial_2009,dullemond_inner_2010,williams_protoplanetary_2011}.
Gas giants presumably finish accreting before the end of disk
dispersal \citep{pollack_formation_1996}.  While rocky planets may
fully form within only a few million years
\citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
over the next 10--100 million years through giant impacts \citep[{\it
e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
The Moon, for instance, may have formed from debris ejected during a
collision between the proto-Earth and a planetesimal during Earth's
first 100 million years \citep{cameron_origin_1976,canup_origin_2001}.

@@

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported
\citep{donati_hj_2016,johns-krull_candidate_2016,biddle_k2_2018,flagg_co_2019}.

@@

If the RM measurements prove that the validated planet is real, a
campaign to measure the mass timed to coincide with TESS sectors 36
and 37 (late March to late May of 2021) would
significantly ease the extraction of the planetary Doppler signal.
The reason is that the RVs, activity indicators, and photometry could
be modeled simultaneously. This would greatly constrain models of
the spot-induced RV signal.  The mass measurement would likely be
worthwhile in order to improve understanding of the planet's
contraction and photoevaporation history.

@@

Resources supporting this work were provided by the NASA High-End
Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
Division at Ames Research Center for the production of the SPOC data
products.

>>>>

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II.
  TOI$\,$837: A Young Validated Saturn-Sized Planet in IC~2602
}

@@

Over the first 100 million years of their lives, exoplanet systems are
expected to undergo major physical and dynamical changes.  For a
typical Sun-like star, the protoplanetary disk disperses within
roughly 1--10 million years
\citep{mamajek_initial_2009,fedele_timescale_2010,dullemond_inner_2010,williams_protoplanetary_2011}.
Gas giants presumably finish accreting before the end of disk
dispersal \citep{pollack_formation_1996}.  While rocky planets may
fully form within only a few million years
\citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
over the next 10--100 million years through giant impacts \citep[{\it
e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
The Moon, for instance, may have formed from debris ejected during a
collision between the proto-Earth and a planetesimal during Earth's
first 100 million years \citep{cameron_origin_1976,canup_origin_2001}.

@@

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.

@@

If the RM measurements prove that the validated planet is real, a
campaign to measure the mass timed to coincide with TESS sectors 36
and 37 (late March to late May of 2021) would significantly ease the
extraction of the planetary Doppler signal.  The reason is that the
RVs, activity indicators, and photometry could be modeled
simultaneously \citep[{\it e.g.},][]{rajpaul_gaussian_2015}. This
would greatly constrain models of the spot-induced RV signal.  The
mass measurement would likely be worthwhile in order to improve
understanding of the planet's contraction and photoevaporation
history.

@@

Resources supporting this work were provided by the NASA High-End
Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
Division at Ames Research Center for the production of the SPOC data
products.
%

A.J.\ and R.B.\ acknowledge support from project IC120009 ``Millennium
Institute of Astrophysics (MAS)'' of the Millenium Science Initiative,
Chilean Ministry of Economy. A.J.\ acknowledges additional support
from FONDECYT project 1171208.
